### 2022-11-20 dissertation/chapters/08-results.tex
🚧 (results): Population size

Similar to before, Figure~\ref{fig:results:heuristic_pool:figures:abalone} provides an illustration of the train and test, loss and accuracy plots for an example classification dataset (abalone) as it relates to the \index{heuristic pool}heuristic pool experimental group. As before, the illustration is provided in log scale and illustrations for the other classification datasets are left out for brevity as they yield similar illustrations.

@@

Figure~\ref{fig:results:heuristic_pool:figures:forest_fires} provides the train and test loss plot for an example regression dataset (forest fires) as it relates to the heuristic pool experimental group. As before, the illustration is provided in log scale and illustrations for the other regression datasets are left out for brevity.

@@

This section provides the empirical results for the experimental group that compares the performance of different variants of the \acs{BHH} as it relates to the \textit{population size} hyper-parameter. Brief discussions follow and illustrations are provided for visual aid. As a reminder, five different population sizes are considered. These include population sizes of 5, 10, 15, 20, and 25.

Table \ref{tab:results:population:metrics} provides the ranked performance, per dataset, of each of the \acs{BHH} population size configurations. Similar to before, the performance rank is calculated as the average rank produced by each population size configuration, for all datasets, over all runs and all training epochs.

@@

Table \ref{tab:results:population:metrics} show that that a smaller population size mostly produces the best results, with statistically significant differences on the adult, bike and car datasets. A population size of 10, slightly higher than the default of 5 is preferred for the forest fires and housing datasets.

@@

Figure~\ref{fig:results:population:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each population size configuration as it relates to all datasets, across all runs. It is shown that there is no overall statistical significant difference between population sizes and the population size hyper-parameter is problem specific.

@@

Similar to before, Figure~\ref{fig:results:population:figures:mushroom} provides the train and test, loss and accuracy plot for an example classification dataset (mushroom) as it relates to the population size experimental group. As before, the illustration is provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_population/figures/train/loss/mushroom.pdf}
		\caption{Train log loss}
		\label{fig:results:population:figures:loss:train:mushroom}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_population/figures/test/loss/mushroom.pdf}
		\caption{Test log loss}
		\label{fig:results:population:figures:loss:test:mushroom}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_population/figures/train/accuracy/mushroom.pdf}
		\caption{Train log accuracy}
		\label{fig:results:population:figures:accuracy:train:mushroom}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_population/figures/test/accuracy/mushroom.pdf}
		\caption{Test log accuracy}
		\label{fig:results:population:figures:accuracy:test:mushroom}
	\end{subfigure}
	\par\bigskip
	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations of the population size hyper-parameter on the mushroom dataset over 30 epochs, illustrated in log scale.}
	\label{fig:results:population:figures:mushroom}
\end{figure}

As a reminder, the experimental group for population sizes only varies the population size hyper-parameter and all other hyper-parameters remain the same between configurations. As such, all population size configurations make use of the \index{heuristic pool}heuristic pool configuration that includes all the low-level heuristics, including gradient-based \index{heuristic}heuristics and \index{meta-heuristic}meta-heuristics. This explains the sporadic results in Figure \ref{fig:results:population:figures:loss:test:mushroom}. Note that the accuracy is almost 100\% and that these sporadic results are simply a result of an attempt to further improve performance even more, by exploring the heuristic space more. Since there is not much room for more improvement, the \acs{BHH} is bound to try different heuristic that yield sub-optimal results.

Figure~\ref{fig:results:population:figures:student_performance} provides the train and test loss plot for an example regression dataset (student performance) as it relates to the population size experimental group. As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_population/figures/train/loss/student_performance.pdf}
		\caption{Train log loss}
		\label{fig:results:population:figures:loss:train:student_performance}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_population/figures/test/loss/student_performance.pdf}
		\caption{Test log loss}
		\label{fig:results:population:figures:loss:test:student_performance}
	\end{subfigure}
	\par\bigskip
	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations of the population size hyper-parameter on the student performance dataset over 30 epochs, illustrated in log scale.}
	\label{fig:results:population:figures:student_performance}
\end{figure}

From Figure~\ref{fig:results:population:figures:loss:train:student_performance} it can be seen that the \acs{BHH} with a small population size of 5 starts to diverge away from optimal results as it explores more options in attempt to provide better solutions. Divergence can be eliminated by means of an early stopping strategy.

@@

Similar to before, Figure~\ref{fig:results:credit:figures:bank} provides the train and test, loss and accuracy plot for an example classification dataset (bank) as it relates to the credit assignment strategy experimental group. As before, the illustration is provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_credit/figures/train/loss/bank.pdf}
		\caption{Train log loss}
		\label{fig:results:credit:figures:loss:train:bank}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_credit/figures/test/loss/bank.pdf}
		\caption{Test log loss}
		\label{fig:results:credit:figures:loss:test:bank}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_credit/figures/train/accuracy/bank.pdf}
		\caption{Train log accuracy}
		\label{fig:results:credit:figures:accuracy:train:bank}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_credit/figures/test/accuracy/bank.pdf}
		\caption{Test log accuracy}
		\label{fig:results:credit:figures:accuracy:test:bank}
	\end{subfigure}
	\par\bigskip
	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations of the credit assignment strategy hyper-parameter on the bank dataset over 30 epochs, illustrated in log scale.}
	\label{fig:results:credit:figures:bank}
\end{figure}

@@

Figure~\ref{fig:results:credit:figures:housing} provides the train and test loss plot for an example regression dataset (housing) as it relates to the credit assignment strategy experimental group. As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_credit/figures/train/loss/housing.pdf}
		\caption{Train log loss}
		\label{fig:results:credit:figures:loss:train:housing}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_credit/figures/test/loss/housing.pdf}
		\caption{Test log loss}
		\label{fig:results:credit:figures:loss:test:housing}
	\end{subfigure}
	\par\bigskip
	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations of the credit assignment strategy hyper-parameter on the housing dataset over 30 epochs, illustrated in log scale.}
	\label{fig:results:credit:figures:housing}
\end{figure}

@@

Similar to before, Figure~\ref{fig:results:reselection:figures:car} provides the train and test, loss and accuracy plot for an example classification dataset (car) as it relates to the reselection interval experimental group. As before, the illustration is provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_reselection/figures/train/loss/car.pdf}
		\caption{Train log loss}
		\label{fig:results:reselection:figures:loss:train:car}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_reselection/figures/test/loss/car.pdf}
		\caption{Test log loss}
		\label{fig:results:reselection:figures:loss:test:car}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_reselection/figures/train/accuracy/car.pdf}
		\caption{Train log accuracy}
		\label{fig:results:reselection:figures:accuracy:train:car}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_reselection/figures/test/accuracy/car.pdf}
		\caption{Test log accuracy}
		\label{fig:results:reselection:figures:accuracy:test:car}
	\end{subfigure}
	\par\bigskip
	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations of the reselection interval hyper-parameter on the car dataset over 30 epochs, illustrated in log scale.}
	\label{fig:results:reselection:figures:car}
\end{figure}

Figure~\ref{fig:results:reselection:figures:bike} provides the train and test loss plot for an example regression dataset (bike) as it relates to the reselection interval experimental group. As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_reselection/figures/train/loss/bike.pdf}
		\caption{Train log loss}
		\label{fig:results:reselection:figures:loss:train:bike}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_reselection/figures/test/loss/bike.pdf}
		\caption{Test log loss}
		\label{fig:results:reselection:figures:loss:test:bike}
	\end{subfigure}
	\par\bigskip
	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations of the reselection interval hyper-parameter on the bike dataset over 30 epochs, illustrated in log scale.}
	\label{fig:results:reselection:figures:bike}
\end{figure}

@@

Similar to before, Figure~\ref{fig:results:replay:figures:diabetic} provides the train and test, loss and accuracy plot for an example classification dataset (diabetic) as it relates to the replay window size experimental group. As before, the illustration is provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_replay/figures/train/loss/diabetic.pdf}
		\caption{Train log loss}
		\label{fig:results:replay:figures:loss:train:diabetic}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_replay/figures/test/loss/diabetic.pdf}
		\caption{Test log loss}
		\label{fig:results:replay:figures:loss:test:diabetic}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_replay/figures/train/accuracy/diabetic.pdf}
		\caption{Train log accuracy}
		\label{fig:results:replay:figures:accuracy:train:diabetic}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_replay/figures/test/accuracy/diabetic.pdf}
		\caption{Test log accuracy}
		\label{fig:results:replay:figures:accuracy:test:diabetic}
	\end{subfigure}
	\par\bigskip
	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations of the replay window size hyper-parameter on the diabetic dataset over 30 epochs, illustrated in log scale.}
	\label{fig:results:replay:figures:diabetic}
\end{figure}

Figure~\ref{fig:results:replay:figures:fish_toxicity} provides the train and test loss plot for an example regression dataset (fish toxicity) as it relates to the replay window size experimental group. As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_replay/figures/train/loss/fish_toxicity.pdf}
		\caption{Train log loss}
		\label{fig:results:replay:figures:loss:train:fish_toxicity}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_replay/figures/test/loss/fish_toxicity.pdf}
		\caption{Test log loss}
		\label{fig:results:replay:figures:loss:test:fish_toxicity}
	\end{subfigure}
	\par\bigskip
	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations of the replay window size hyper-parameter on the fish toxicity dataset over 30 epochs, illustrated in log scale.}
	\label{fig:results:replay:figures:fish_toxicity}
\end{figure}

@@

Similar to before, Figure~\ref{fig:results:reanalysis:figures:mushroom} provides the train and test, loss and accuracy plot for an example classification dataset (mushroom) as it relates to the reanalysis interval experimental group. As before, the illustration is provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_reanalysis/figures/train/loss/mushroom.pdf}
		\caption{Train log loss}
		\label{fig:results:reanalysis:figures:loss:train:mushroom}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_reanalysis/figures/test/loss/mushroom.pdf}
		\caption{Test log loss}
		\label{fig:results:reanalysis:figures:loss:test:mushroom}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_reanalysis/figures/train/accuracy/mushroom.pdf}
		\caption{Train log accuracy}
		\label{fig:results:reanalysis:figures:accuracy:train:mushroom}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_reanalysis/figures/test/accuracy/mushroom.pdf}
		\caption{Test log accuracy}
		\label{fig:results:reanalysis:figures:accuracy:test:mushroom}
	\end{subfigure}
	\par\bigskip
	\caption{The train and test, loss and accuracy plot for the experimental group comparing the performance of the \acs{BHH} with different configurations for the reanalysis interval hyper-parameter on the mushroom dataset over 30 epochs, illustrated in log scale.}
	\label{fig:results:reanalysis:figures:mushroom}
\end{figure}

Figure~\ref{fig:results:reanalysis:figures:parkinsons} provides the train and test loss plot for an example regression dataset (parkinsons) as it relates to the renalysis interval experimental group. As before, the illustration is provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.

>>>>

Similar to before, Figure~\ref{fig:results:heuristic_pool:figures:abalone} provides an illustration of the train and test, loss and accuracy plots for an example classification dataset (abalone) as it relates to the \index{heuristic pool}heuristic pool experimental group. As before, the illustrations are provided in log scale and illustrations for the other classification datasets are left out for brevity as they yield similar illustrations.

@@

Figure~\ref{fig:results:heuristic_pool:figures:forest_fires} provides the train and test loss plots for an example regression dataset (forest fires) as it relates to the heuristic pool experimental group. As before, the illustrations are provided in log scale and illustrations for the other regression datasets are left out for brevity.

@@

This section provides the empirical results for the experimental group that compares the performance of different variants of the \acs{BHH} as it relates to the \textit{population size} hyper-parameter. Brief discussions follow and illustrations are provided for visual aid. As a reminder, five different population sizes are considered. These include population sizes of 5, 10, 15, 20, and 25, and experiments are denoted as such.

Table~\ref{tab:results:population:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the population size variants of the \acs{BHH} that was implemented. Similar to before, the test loss is measured at the last epoch for each dataset, over all independent runs.
	\caption{Empirical results showing average test loss and statistics for all population size configurations used by the \acs{BHH} across multiple datasets, for all independent runs and is measured at the last epoch.}

From Table \ref{tab:results:population:metrics:loss} it can be seen that the lowest population size produced mostly the best performance outcomes, yielding the best average test loss for eight of the fourteen datasets. However, the lowest population size also produced the worst performance outcomes for four of the fourteen datasets. From the empirical results that show the average test loss, measured at the last epoch, it is not clear which population size configuration produced the overall best results.

As before, the performance of the different \acs{BHH} population size configurations need to be considered for the entire training process. As such, Table \ref{tab:results:population:metrics:rank} provides the ranked performance, per dataset, of each of the \acs{BHH} population size configurations. Similar to before, the performance rank is calculated as the average rank produced by each population size configuration, for all datasets, over all runs and all training epochs.

@@

From Table \ref{tab:results:population:metrics:rank} it can be seen that a lower population size of five, mostly produced the best results, with exception to the bike and car datasets, for which the lowest population size configuration produced the worst performance, yielding statistically significant differences in outcomes from the other datasets. A larger population size configuration is prefered for the bike and car datasets. Furthermore, a population size configuration of ten, slightly higher than the default of five, is preferred for the forest fires and housing datasets. Finally, the overall normalised average rank is provided at the bottom of the table, showing that a population size of five produced the best performance outcome across all datasets on average.

@@

Figure~\ref{fig:results:population:descriptive:descriptive}, shows the correlation of performance with population size for each dataset. From these illustrations, it can be seen that the correlation between the population size configuration and performance is different for each dataset, suggesting that the population size hyper-parameter is problem specific. However, the overall performance related to each population configuration, across all datasets is not clear from these illustrations.

Figure~\ref{fig:results:population:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each population size configuration as it relates to all datasets, across all runs and epochs. It is shown that there is no overall statistical significant difference between population sizes and thus, it can be concluded that the population size hyper-parameter is problem specific.

@@

Similar to before, Figure~\ref{fig:results:population:figures:mushroom} provides the train and test, loss and accuracy plots for an example classification dataset (mushroom) as it relates to the population size experimental group. As before, the illustrations are provided in log scale and illustrations of train and test loss and accuracy plots for the other classification datasets are left out for brevity as they yield similar illustrations.

\begin{figure}[htbp]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_population/figures/train/loss/mushroom.pdf}
		\caption{Train log loss}
		\label{fig:results:population:figures:loss:train:mushroom}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_population/figures/test/loss/mushroom.pdf}
		\caption{Test log loss}
		\label{fig:results:population:figures:loss:test:mushroom}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_population/figures/train/accuracy/mushroom.pdf}
		\caption{Train log accuracy}
		\label{fig:results:population:figures:accuracy:train:mushroom}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_population/figures/test/accuracy/mushroom.pdf}
		\caption{Test log accuracy}
		\label{fig:results:population:figures:accuracy:test:mushroom}
	\end{subfigure}
	\par\bigskip
	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the population size hyper-parameter on the mushroom dataset over 30 epochs, illustrated in log scale.}
	\label{fig:results:population:figures:mushroom}
\end{figure}

As a reminder, the experimental group for population sizes only varies the population size hyper-parameter and all other hyper-parameters remain the same between configurations. As such, all population size configurations make use of the \index{heuristic pool}heuristic pool configuration that includes all the low-level heuristics, including gradient-based \index{heuristic}heuristics and \index{meta-heuristic}meta-heuristics.

Divergence of the training loss can be observed in Figure \ref{fig:results:population:figures:loss:test:mushroom}. Note that, despite the divergence of training loss, the accuracy is still almost 100\% and that these divergent behaviours are simply a result of an attempt to further improve performance, by exploring the heuristic space more. For example, heuristics could have momentum as a result of good training progression thus far, but then overshoot good solutions after \index{heuristic}heuristic reselection. Overshooting good solutions then causes the \index{heuristic}heuristics to struggle to converge back to good solutions, especially if many different \index{heuristic}heuristics are selected in quick succession. A suggestion to this problem is to implement a move-acceptance strategy as was mentioned before. At the nineth epoch, the \acs{BHH} fails to produce better solutions on the training set. Since there is not much room for more improvement, the \acs{BHH} is bound to try different \index{heuristic}heuristics that yield sub-optimal results. From this point onwards, the \acs{BHH} finds slightly better results on the train set, and as a result, produces volatile performance on the test set.

Figure~\ref{fig:results:population:figures:student_performance} provides the train and test loss plots for an example regression dataset (student performance) as it relates to the population size experimental group. As before, the illustrations are provided in log scale and illustration of train and test loss plots for the other regression datasets are left out for brevity.

\begin{figure}[htbp]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_population/figures/train/loss/student_performance.pdf}
		\caption{Train log loss}
		\label{fig:results:population:figures:loss:train:student_performance}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_population/figures/test/loss/student_performance.pdf}
		\caption{Test log loss}
		\label{fig:results:population:figures:loss:test:student_performance}
	\end{subfigure}
	\par\bigskip
	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the population size hyper-parameter on the student performance dataset over 30 epochs, illustrated in log scale.}
	\label{fig:results:population:figures:student_performance}
\end{figure}

From Figure~\ref{fig:results:population:figures:loss:train:student_performance} it can be seen that the \acs{BHH} with a low population size of five starts to diverge away from optimal results as it explores different \index{heuristic}heuristics in an attempt to provide better solutions. Divergence can be eliminated by means of an early stopping strategy as well as a move-acceptance strategy as mentioned before.

@@

Similar to before, Figure~\ref{fig:results:credit:figures:bank} provides the train and test, loss and accuracy plots for an example classification dataset (bank) as it relates to the credit assignment strategy experimental group. As before, the illustrations are provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_credit/figures/train/loss/bank.pdf}
		\caption{Train log loss}
		\label{fig:results:credit:figures:loss:train:bank}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_credit/figures/test/loss/bank.pdf}
		\caption{Test log loss}
		\label{fig:results:credit:figures:loss:test:bank}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_credit/figures/train/accuracy/bank.pdf}
		\caption{Train log accuracy}
		\label{fig:results:credit:figures:accuracy:train:bank}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_credit/figures/test/accuracy/bank.pdf}
		\caption{Test log accuracy}
		\label{fig:results:credit:figures:accuracy:test:bank}
	\end{subfigure}
	\par\bigskip
	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the credit assignment strategy hyper-parameter on the bank dataset over 30 epochs, illustrated in log scale.}
	\label{fig:results:credit:figures:bank}
\end{figure}

@@

Figure~\ref{fig:results:credit:figures:housing} provides the train and test loss plots for an example regression dataset (housing) as it relates to the credit assignment strategy experimental group. As before, the illustrations are provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_credit/figures/train/loss/housing.pdf}
		\caption{Train log loss}
		\label{fig:results:credit:figures:loss:train:housing}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_credit/figures/test/loss/housing.pdf}
		\caption{Test log loss}
		\label{fig:results:credit:figures:loss:test:housing}
	\end{subfigure}
	\par\bigskip
	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the credit assignment strategy hyper-parameter on the housing dataset over 30 epochs, illustrated in log scale.}
	\label{fig:results:credit:figures:housing}
\end{figure}

@@

Similar to before, Figure~\ref{fig:results:reselection:figures:car} provides the train and test, loss and accuracy plots for an example classification dataset (car) as it relates to the reselection interval experimental group. As before, the illustrations are provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_reselection/figures/train/loss/car.pdf}
		\caption{Train log loss}
		\label{fig:results:reselection:figures:loss:train:car}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_reselection/figures/test/loss/car.pdf}
		\caption{Test log loss}
		\label{fig:results:reselection:figures:loss:test:car}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_reselection/figures/train/accuracy/car.pdf}
		\caption{Train log accuracy}
		\label{fig:results:reselection:figures:accuracy:train:car}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_reselection/figures/test/accuracy/car.pdf}
		\caption{Test log accuracy}
		\label{fig:results:reselection:figures:accuracy:test:car}
	\end{subfigure}
	\par\bigskip
	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the reselection interval hyper-parameter on the car dataset over 30 epochs, illustrated in log scale.}
	\label{fig:results:reselection:figures:car}
\end{figure}

Figure~\ref{fig:results:reselection:figures:bike} provides the train and test loss plots for an example regression dataset (bike) as it relates to the reselection interval experimental group. As before, the illustrations are provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_reselection/figures/train/loss/bike.pdf}
		\caption{Train log loss}
		\label{fig:results:reselection:figures:loss:train:bike}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_reselection/figures/test/loss/bike.pdf}
		\caption{Test log loss}
		\label{fig:results:reselection:figures:loss:test:bike}
	\end{subfigure}
	\par\bigskip
	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the reselection interval hyper-parameter on the bike dataset over 30 epochs, illustrated in log scale.}
	\label{fig:results:reselection:figures:bike}
\end{figure}

@@

Similar to before, Figure~\ref{fig:results:replay:figures:diabetic} provides the train and test, loss and accuracy plots for an example classification dataset (diabetic) as it relates to the replay window size experimental group. As before, the illustrations are provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_replay/figures/train/loss/diabetic.pdf}
		\caption{Train log loss}
		\label{fig:results:replay:figures:loss:train:diabetic}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_replay/figures/test/loss/diabetic.pdf}
		\caption{Test log loss}
		\label{fig:results:replay:figures:loss:test:diabetic}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_replay/figures/train/accuracy/diabetic.pdf}
		\caption{Train log accuracy}
		\label{fig:results:replay:figures:accuracy:train:diabetic}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_replay/figures/test/accuracy/diabetic.pdf}
		\caption{Test log accuracy}
		\label{fig:results:replay:figures:accuracy:test:diabetic}
	\end{subfigure}
	\par\bigskip
	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the replay window size hyper-parameter on the diabetic dataset over 30 epochs, illustrated in log scale.}
	\label{fig:results:replay:figures:diabetic}
\end{figure}

Figure~\ref{fig:results:replay:figures:fish_toxicity} provides the train and test loss plots for an example regression dataset (fish toxicity) as it relates to the replay window size experimental group. As before, the illustrations are provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_replay/figures/train/loss/fish_toxicity.pdf}
		\caption{Train log loss}
		\label{fig:results:replay:figures:loss:train:fish_toxicity}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_replay/figures/test/loss/fish_toxicity.pdf}
		\caption{Test log loss}
		\label{fig:results:replay:figures:loss:test:fish_toxicity}
	\end{subfigure}
	\par\bigskip
	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the replay window size hyper-parameter on the fish toxicity dataset over 30 epochs, illustrated in log scale.}
	\label{fig:results:replay:figures:fish_toxicity}
\end{figure}

@@

Similar to before, Figure~\ref{fig:results:reanalysis:figures:mushroom} provides the train and test, loss and accuracy plots for an example classification dataset (mushroom) as it relates to the reanalysis interval experimental group. As before, the illustrations are provided in log scale and illustrations of train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_reanalysis/figures/train/loss/mushroom.pdf}
		\caption{Train log loss}
		\label{fig:results:reanalysis:figures:loss:train:mushroom}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_reanalysis/figures/test/loss/mushroom.pdf}
		\caption{Test log loss}
		\label{fig:results:reanalysis:figures:loss:test:mushroom}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_reanalysis/figures/train/accuracy/mushroom.pdf}
		\caption{Train log accuracy}
		\label{fig:results:reanalysis:figures:accuracy:train:mushroom}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_reanalysis/figures/test/accuracy/mushroom.pdf}
		\caption{Test log accuracy}
		\label{fig:results:reanalysis:figures:accuracy:test:mushroom}
	\end{subfigure}
	\par\bigskip
	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations for the reanalysis interval hyper-parameter on the mushroom dataset over 30 epochs, illustrated in log scale.}
	\label{fig:results:reanalysis:figures:mushroom}
\end{figure}

Figure~\ref{fig:results:reanalysis:figures:parkinsons} provides the train and test loss plots for an example regression dataset (parkinsons) as it relates to the renalysis interval experimental group. As before, the illustrations are provided in log scale and illustration of train and test loss plots for other regression datasets are left out for brevity.

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_reanalysis/figures/train/loss/parkinsons.pdf}
		\caption{Train log loss}
		\label{fig:results:reanalysis:figures:loss:train:parkinsons}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_reanalysis/figures/test/loss/parkinsons.pdf}
		\caption{Test log loss}
		\label{fig:results:reanalysis:figures:loss:test:parkinsons}
	\end{subfigure}
	\par\bigskip
	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations for the reanalysis interval hyper-parameter on the parkinsons dataset over 30 epochs, illustrated in log scale.}
	\label{fig:results:reanalysis:figures:parkinsons}
\end{figure}
